On existence of integral point sets and their diameter bounds \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2020-01-02 pps-linear-bound/pps-linear-lower-bound.tex
[J220] Improving structure of the Section devoted to sets with side 1
[J220] Note about Section structure

TODO: note about Section structure.

@@

\section{Constructing integral point sets}

@@

@@

>>>>

Sections 2--4 are devoted to the linear lower bound.
Each Section consists of 2 Subsections: General results an Special results.
In General results, avoid attempts to provide tight estimates;
such attempts are done in Special results.

Section 5 is devoted to integral point sets with distance 1 and has its own structure.

@@

\section{Integral point sets with distance 1}

\subsection{Constructing planar integral point sets with distance 1}

@@

\subsection{Description of planar integral point sets with distance 1}

@@

\subsection{Higher dimensions}
